---
title: "Final Project"
author: "Alejandro Pacheco"
date: "2022-12-06"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(anyflights)
library(dplyr)
library(readr)
library(lubridate)
library(plotly)
library(ggplot2)
```

## Data frame code
```{r}
LAXflights<-read.csv("C:/Users/Alejandro Pacheco/OneDrive - Emory University/Documents/LAXflights.csv",header=TRUE,stringsAsFactors = FALSE)
#LAXflights

ATLflights<-read.csv("C:/Users/Alejandro Pacheco/OneDrive - Emory University/Documents/ATLflights.csv",header=TRUE,stringsAsFactors = FALSE)

DAL<-read.csv("C:/Users/Alejandro Pacheco/OneDrive - Emory University/Documents/DAL.csv",header=TRUE,stringsAsFactors = FALSE)
#ATLflights

write.csv(LAXflights, file = "LAXflights.csv")
write.csv(ATLflights, file = "ATLflights.csv")

AvgDALPrice <- mutate(DAL, avg_daily = (High + Low)/2)

CanceledLAX <- mutate(LAXflights, canceled = is.na(dep_time))
CanceledATL <- mutate(ATLflights, canceled = is.na(dep_time))

CanceledLAX <- mutate(CanceledLAX, flight_date = as_date(CanceledLAX$time_hour))
CanceledATL <- mutate(CanceledATL, flight_date = as_date(CanceledATL$time_hour))


CanceledCountLAX <- 0
OtherCountLAX <- 0
cancelPropLAX = vector()

CanceledCountATL <- 0

OtherCountATL <- 0
cancelPropATL = vector()
k <- 1
i <- 1

for(j in 1:1096) {
  for(k in k:length(CanceledLAX$flight_date)) {
    if((j-j%/%731+j%/%366)%%366 == yday(CanceledLAX$flight_date[k]) | j == 731) {
      if (CanceledLAX$canceled[k] == TRUE) {
        CanceledCountLAX <- CanceledCountLAX + 1
      }
      else {
        OtherCountLAX <- OtherCountLAX + 1
      }
    }
    else {
      break
    }
  }
  cancelPropLAX[j] <- CanceledCountLAX / (OtherCountLAX+CanceledCountLAX)
}

for(j in 1:1096) {
  for(i in i:length(CanceledATL$flight_date)) {
    if((j-j%/%731+j%/%366)%%366 == yday(CanceledATL$flight_date[i]) | j == 731) {
      if (CanceledATL$canceled[i] == TRUE) {
        CanceledCountATL <- CanceledCountATL + 1
      }
      else {
        OtherCountATL <- OtherCountATL + 1
      }
    }
    else {
      break
    }
  }
  cancelPropATL[j] <- CanceledCountATL / (OtherCountATL+CanceledCountATL)
}

cancelProp <- data.frame(cancelPropATL, cancelPropLAX)
```

## Average Stock Price for Delta
```{r}
ggplot(DAL,aes(x=Date,y=Close))+
  geom_line()
```




## Percentage of flights cancelled for the past 3 years   
```{r}
cancel<-cancelPropATL[1:755]
AvgDALPrice <- mutate(DAL, avg_daily = (High + Low)/2)
new_table<-data.frame(cancel,AvgDALPrice)

ggplot(new_table,aes(x=Date,y=cancel))+
  geom_line()
```


## Relationship between average stock price and the percentage of cancelled flights
```{r}
cancel<-cancelPropATL[1:755]
AvgDALPrice <- mutate(DAL, avg_daily = (High + Low)/2)
new_table<-data.frame(cancel,AvgDALPrice)


new_table %>%
  plot_ly(x = ~cancel, y = ~avg_daily) %>%
  filter(cancel<0.0081) %>%
  add_lines()
```


## Cancelation percentage based on the first three months of Covid
```{r}
cancel<-cancelPropATL[1:755]
AvgDALPrice <- mutate(DAL, avg_daily = (High + Low)/2)
new_table<-data.frame(cancel,AvgDALPrice)

new_table[60:120,1:9]%>%
  ggplot(aes(x=Date,y=cancel))+
  geom_line()
```

## Average stock price during the first three months of covid
```{r}
cancel<-cancelPropATL[1:755]
AvgDALPrice <- mutate(DAL, avg_daily = (High + Low)/2)
new_table<-data.frame(cancel,AvgDALPrice)

new_table[60:120,1:9]%>%
  ggplot(aes(x=Date,y=avg_daily))+
  geom_line()
```


## Cronological view of the relationship between flight cancelationsand Delta stock at LAX airport
```{r}
cancel<-cancelPropATL[1:755]
AvgDALPrice <- mutate(DAL, avg_daily = (High + Low)/2)
new_table<-data.frame(cancel,AvgDALPrice)

Date<-new_table$Date[60:400]
AvgStockPrice<-new_table$cancel[60:400]*6200
y2<-new_table$avg_daily[60:400]
df<-data.frame(AvgStockPrice,y2)

ggplot(df,aes(Date))+
  geom_line(aes(y=AvgStockPrice),color="red")+
  geom_line(aes(y=y2),color="blue")
```

